### 2014-05-21 acks.tex
Small fixes
Add Garrett and Juliusz to acks

I owe much to my time in the Wall Street Journal's late Boston
bureau. My editors Gary Putka and Dan Golden, and my colleague Charles
Forelle, taught me how to develop a nose for investigations and how to
tell a story. Gary's ``dun-colored warren of cubicles'' represented a
journalistic Camelot and was as intellectually challenging as any lab
in academia.

Many others helped to develop the ideas in this work, especially Chris
Amato, Andrew McGregor, Tim Shepard, John Wroclawski, Bill McCloskey, Josh Mandel,
Carrie Niziolek, Damon Wischik, Hariharan Rahul, Chris Lesniewski,
Vikash Mansinghka, Eric Jonas, Marissa Cheng, and Allie Brownell.

>>>>

I owe much to my time in the Wall Street Journal's late Boston
bureau. My editors Gary Putka and Dan Golden, and my colleague Charles
Forelle, taught me how to develop a nose for investigations and how to
tell a story. Gary's ``dun-colored warren of cubicles'' represented a
journalistic Camelot and was as intellectually challenging as any lab.

Many others helped to develop the ideas in this work, especially
Pratiksha Thaker, Chris Amato, Andrew McGregor, Tim Shepard, John
Wroclawski, Bill McCloskey, Josh Mandel, Carrie Niziolek, Damon
Wischik, Hariharan Rahul, Garrett Wollman, Juliusz Chroboczek, Chris
Lesniewski, Vikash Mansinghka, Eric Jonas, Marissa Cheng, and Allie
Brownell.
